 \section{Conclusion and Future Work}\label{sec:Conclusion}
This paper presented an autonomous technique for geophone placement, recording, and retrieval. The system enables automating a job that currently requires large teams of manual laborers. Three components were introduced, SeismicDarts, a mobile SeismicSpider, and a deployment unit.
Field and laboratory hardware experiments demonstrated the efficacy of the robotic team compared to traditional techniques. 
The SeismicDart's output is comparable to well-planted geophones. 
For hard surfaces where the SeismicDart could not penetrate, we presented an autonomous alternative, the SeismicSpider.  
The SeismicSpider is mobile, can actively adjust its sensors to ensure ground contact and vertical placement, and can be deployed and retrieved by UAVs.

Autonomous deployment was conducted using GPS, proving human involvement could be minimized by adopting the proposed technique. 
Hardware experiments compared the autonomous system to manual planting and ballistic deployment.
Simulation studies show time and cost savings over traditional manual techniques.

Future systems should be weatherized and optimized for cost, robustness, range, and speed. 
Soil maps could be used to plan a survey, allocating SeismicSpiders to rocky or forested areas and SeismicDarts to penetrable soils. 
These maps can be made more accurate using drone-carried ground penetrating radar \cite{merz2015new}. Alternatively, the  SeismicDart's internal accelerometer also provides feedback on the quality of the plant. As shown in Fig.~\ref{fig:AnglePlotIndoors}, increasing angular deviations indicate a higher drop height is needed.  

