%  compress using: gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH      -sOutputFile=SeismicRALcompressed.pdf RA-L2016.pdf
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.
%\IEEEoverridecommandlockouts
%\documentclass[conference]{IEEEtran}
\newcommand{\subparagraph}{}
\usepackage{epsfig,graphicx,cite}
\usepackage{psfrag}
\usepackage[small,compact]{titlesec}
\usepackage{wrapfig}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{verbatim,amsfonts,amsmath,amssymb}
\usepackage{fancyhdr}
\usepackage{mathbbold}
\usepackage{bbm}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{amssymb,amsmath,bm,makecell}
\usepackage{indentfirst}
\usepackage{overpic}
\newcommand{\figwid}{0.22\columnwidth}

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}



\usepackage{mathtools}
\usepackage[font=footnotesize]{caption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tabulary}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{fancyhdr}
%\usepackage[hypertex]{hyperref}
\usepackage[hidelinks]{hyperref}
%\IEEEoverridecommandlockouts
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{times,verbatim,amsfonts,amsmath,color}
%\newtheorem{definition}{\textbf{Definition}}
%\newtheorem{lemma}{\textbf{Lemma}}
%\newtheorem{proof}{\textbf{Proof}}
%\newtheorem{theorem}{\textbf{Theorem}}
%\newtheorem{example}{\textbf{Example}}
%\newtheorem{proposition}{\textbf{Proposition}}
%\newtheorem{remark}{\textbf{Remark}}
%\newtheorem{corrolary}{\textbf{Corrolary}}
%\newtheorem{ex}{\textbf{EX}}
\usepackage{overpic}
\graphicspath{{./},{./pictures/}}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\usepackage[table,xcdraw]{xcolor}
\newcommand{\todo}[1]{ \textcolor{red}{\ttfamily#1}}
\newcommand{\todobox}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
\let\labelindent\relax \usepackage{enumitem}





\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\LARGE \bf A Heterogeneous Robotics Team for Large-Scale Seismic Sensing} 

\author{Srikanth K. V. Sudarshan$^{1}$,
Victor Montano$^{1}$,
An Nguyen$^{1}$,\\ 
Michael McClimans$^{2}$,
Li Chang$^{2}$,
Robert Stewart$^{2}$, and
 Aaron T. Becker$^{1}$% <-this % stops a space
\thanks{*This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.}% <-this % stops a space
\thanks{$^{1}$Department of Electrical and Computer Engineering,}
\thanks{$^{2}$Department of Earth and Atmospheric Sciences,\\ University of Houston, 4800 Calhoun Rd, Houston, TX 77004, USA
        {\tt\small \{skvenkatasudarshan, vjmontano, anguyen43, msmcclimans, lchang13, rrstewart, atbecker\}@uh.edu}}%
}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


\begin{abstract} 
Seismic surveying requires placing a large number of sensors (geophones) in a grid pattern, triggering a seismic event, and recording vibration readings. 
 The goal of the surveying is often to locate subsurface resources.  
Traditional seismic surveying employs human laborers for sensor placement and retrieval. 
The major drawbacks of surveying with human deployment are the high costs and time, and risks to humans due to explosives, terrain, and climatic conditions.
We propose an autonomous, heterogeneous sensor deployment system using unmanned aerial vehicles (UAVs) to deploy mobile and immobile sensors.
The proposed system begins to overcome some of the problems associated with traditional systems.  
This paper provides detailed analysis and comparison with traditional survey techniques. 
Hardware experiments and simulations show promise for automation reducing cost and time. 
 Autonomous aerial systems will have a substantial contribution to make in future seismic surveys. 
\end{abstract}

\input{Introduction}
%
\input{RelatedWork}
%
\input{SmartDarts}
%
\input{SeismicSpider}
%
\input{UAV}
%
\input{Comparison}
%
\input{conclusion}


\bibliographystyle{IEEEtran}
\bibliography{./bibs/Match}

% that's all folks
\end{document}


