%  compress using: gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH      -sOutputFile=foo-compressed.pdf SeismicDrones.pdf
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
%\IEEEoverridecommandlockouts
%\documentclass[conference]{IEEEtran}
\newcommand{\subparagraph}{}
\usepackage{epsfig,graphicx,cite}
\usepackage{psfrag}
\usepackage[small,compact]{titlesec}
\usepackage{wrapfig}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{verbatim,amsfonts,amsmath,amssymb}
\usepackage{fancyhdr}
\usepackage{mathbbold}
\usepackage{bbm}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{amssymb,amsmath,bm,makecell}
\usepackage{indentfirst}
\usepackage{overpic}
\newcommand{\figwid}{0.22\columnwidth}

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}



\usepackage{mathtools}
\usepackage[font=footnotesize]{caption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tabulary}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{fancyhdr}
%\usepackage[hypertex]{hyperref}
\usepackage[hidelinks]{hyperref}
%\IEEEoverridecommandlockouts
\usepackage{cite,url,subfigure,epsfig,graphicx}
\usepackage{times,verbatim,amsfonts,amsmath,color}
%\newtheorem{definition}{\textbf{Definition}}
%\newtheorem{lemma}{\textbf{Lemma}}
%\newtheorem{proof}{\textbf{Proof}}
%\newtheorem{theorem}{\textbf{Theorem}}
%\newtheorem{example}{\textbf{Example}}
%\newtheorem{proposition}{\textbf{Proposition}}
%\newtheorem{remark}{\textbf{Remark}}
%\newtheorem{corrolary}{\textbf{Corrolary}}
%\newtheorem{ex}{\textbf{EX}}
\usepackage{overpic}
\graphicspath{{./},{./pictures/}}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\usepackage[table,xcdraw]{xcolor}
\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
\let\labelindent\relax \usepackage{enumitem}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Seismic Surveying with Drone-Mounted Geophones } 

\author[1]{\rm Srikanth K. V. Sudarshan}
\author[1]{\rm Li Huang}
\author[2]{\rm Li Chang}
\author[2]{\rm Robert Stewart}
\author[1]{\rm Aaron T. Becker}
\affil[1]{Department of Electrical and Computer Engineering}
\affil[2]{Department of Earth and Atmospheric Sciences}
\affil[ ]{University of Houston}
\affil[ ]{4800 Calhoun Rd, Houston, TX 77004}
\affil[ ]{\textit {\{skvenkatasudarshan, lhuang21, lchang13, rrstewar, atbecker\}@uh.edu}}
% make the title area
\maketitle

%(http://www.eoearth.org/view/article/155968/) Seismic exploration is the search for commercially economic subsurface deposits of crude oil, natural gas, and minerals by the recording, processing, and interpretation of artificially induced shock waves in the earth
\begin{abstract}

Seismic imaging is the primary technique (and industries) for subsurface exploration. It involves generating a vibration which propagates into the ground, echoes, and is recorded using motion sensors. Often sites of resource or rescue interest may be difficult or hazardous to access. In addition, traditional seismic imaging techniques rely heavily on manual labor to plant sensors, lay miles of cabling, and then collect the sensors. Thus, there is a substantial need for unmanned sensors that can be deployed by air and potentially in large numbers. This paper presents a working prototype of autonomous drones equipped with geophone vibration sensors that can fly to a site, land, listen for echoes and vibrations, store the information on-board, and subsequently return to home base.
The design uses four geophone sensors (with spikes) in place of the landing gear.  This provides a stable landing attitude, redundancy in sensing, and ensures the geophones are oriented perpendicular to the ground. The paper describes hardware experiments demonstrating the efficacy of this technique and a comparison with traditional manual techniques. The performance of the seismic drone was comparable to a well planted geophone, proving the drone mount system is a feasible alternative to traditional seismic sensors.

\end{abstract}
%\begin{IEEEkeywords} Data Acquisition, Geophones, Quadcopters, Seismic Exploration \end{IEEEkeywords}

\input{introduction}
%
\input{relatedwork}
%
\input{experiments}
%
\input{conclusion}


\bibliographystyle{IEEEtran}
\bibliography{./bibs/Match}

% that's all folks
\end{document}


